paper

### 2022-03-29 outputs/paper.Rmd
Include figures

```{r data, echo=FALSE, fig.cap="Data"}
ghana %>%
  group_by(character) %>%
  summarise(sum = sum(number_of_employed_women))
```

Table \@ref(tab:data) shows that 3,566 participated the survey, but there are 3 whom did not answer their employment status, etc.

>>>>

```{r total, echo=FALSE, fig.cap="Data"}
ghana %>%
  mutate(
    character = factor(character,
                       levels=c("Residence",
                                "Region",
                                "Mother\'s_education",
                                "Work_status",
                                "Occupation",
                                "Employment_status",
                                "Total"
                                )
                       )
           ) %>%
  group_by(character) %>%
  summarise(sum = sum(number_of_employed_women))
```

Table \@ref(tab:total) shows that 3,566 participated the survey, but there are 3 whom did not answer their employment status, etc.

```{r data, echo=FALSE}
ghana %>%
  select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, character) %>%
  slice(1:10) %>%
  kable(caption='A subset of key features',
        col.names = c('Background', 'No child under six', '1+ child under six', 
                      'Child\'s caretaker - respondent', 'Character'),
        digits = 1,
        booktabs = FALSE,
        linesep = "")
```

# Results

## Mother's education

```{r motheredu, echo=FALSE, message=FALSE, fig.cap="Mother's Education level"}
mother_edu <-
  ghana %>%
  filter(character=="Mother\'s_education") %>%
  mutate(
    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
  )

mother_edu_tb<-
  tibble(
    background =
      c(""),
    child_under_six = 
      c("")
  )

for (r in 1:nrow(mother_edu)){
  level <- mother_edu$background[r]
  edu <-
    tibble(
      background = 
        c(
          rep(level, mother_edu$number_of_employed_women[r])
        ),
      child_under_six = 
        c(
          rep("No_child_under_six", mother_edu$no_child_under_six[r]),
          rep("One_more_child_under_six", mother_edu$one_more_child_under_six[r])
        )
      )

  mother_edu_tb <- bind_rows(mother_edu_tb, edu)
  rm(level,
     edu)
}
rm(r)
mother_edu_tb <- mother_edu_tb[-c(1),]

mother_edu_tb <-
  mother_edu_tb %>%
  mutate(
    background = factor(background,
                        levels = c('No_education',
                                   'Primary',
                                   'Middle',
                                   'Secondary+')
                        )
    )

mother_edu_tb %>%
  ggplot(mapping=aes(x=background, fill=child_under_six)) +
  geom_bar(position='dodge') +
  theme_minimal() +
  labs(x='education level', y='number of employed', fill='Child under six') +
  scale_x_discrete(labels = c("No_education" = "No education")) +
  scale_fill_discrete(labels = c("No child under six", 
                                 "One or more child under six"))

rm(mother_edu_tb)
```

Figure \@ref(fig:motheredu) shows that there are less women who studied more than secondary school, and only the secondary+ turned out to be more likely to have no child under six.

```{r mothereduchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by mother's education level"}
mother_edu <-
  mother_edu %>%
  mutate(
    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
    ) %>%
  mutate(
    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
  ) %>%
  select(-caretaker_other_male_child) %>%
  rename(caretaker_other_child = caretaker_other_female_child)

mother_edu_tb<-
  tibble(
    background =
      c(""),
    child_caretaker = 
      c("")
  )

# clean_caretaker <- 
#   mother_edu %>%
#   select(starts_with("caretaker_")) %>%
#   mutate(sum_caretaker = rowSums(.))
# clean_caretaker$num <-
#   mother_edu$one_more_child_under_six

mother_edu[3, 13] <- 0
mother_edu[3, 11] <- mother_edu[3, 11] - 1

for (r in 1:nrow(mother_edu)){
  level <- mother_edu$background[r]
  edu <-
    tibble(
      background = 
        c(
          rep(level, mother_edu$one_more_child_under_six[r])
        ),
      child_caretaker = 
        c(
          rep("respondent", mother_edu$caretaker_respondent[r]),
          rep("partner", mother_edu$caretaker_partner[r]),
          rep("other_relative", mother_edu$caretaker_other_relative[r]),
          rep("neighbor", mother_edu$caretaker_neighbor[r]),
          rep("hired", mother_edu$caretaker_hired[r]),
          rep("child_in_school", mother_edu$caretaker_child_in_school[r]),
          rep("other_child", mother_edu$caretaker_other_child[r]),
          rep("not_worked_since_birth", mother_edu$caretaker_not_worked_since_birth[r]),
          rep("other", mother_edu$caretaker_other[r]),
          rep("missing", mother_edu$caretaker_missing[r])
        )
      )

  mother_edu_tb <- bind_rows(mother_edu_tb, edu)
  rm(level,
     edu)
}
rm(r)
mother_edu_tb <- mother_edu_tb[-c(1),]

mother_edu_tb <-
  mother_edu_tb %>%
  mutate(
    background = factor(background,
                        levels = c('No_education',
                                   'Primary',
                                   'Middle',
                                   'Secondary+')
                        ),
    child_caretaker = factor(child_caretaker,
                             levels = c('respondent',
                                        'partner',
                                        'other_relative',
                                        'neighbor',
                                        'hired',
                                        'child_in_school',
                                        'other_child',
                                        'not_worked_since_birth',
                                        'other',
                                        'missing')
                             )
    )

mother_edu_tb %>%
  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
  geom_bar() +
  theme_minimal() +
  labs(x='',
       y='number of employed',
       caption = 'Respondent is currently employed but has not worked since last birth.') +
  theme(axis.text.x = element_text(angle=15), legend.position='none') +
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent", 
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired",
        "child_in_school" = "schooling",
        "other_child" = "siblings",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  ) +
  facet_wrap(vars(background),
             dir = "v",
             scales = "free",
             labeller = labeller(background = 
                                   c("No_education" = "No education",
                                     "Primary" = "Primary",
                                     "Middle" = "Middle",
                                     "Secondary+" = "Secondary+")
                                 )
  )

rm(mother_edu_tb)
```

## Work status

```{r workstatus, echo=FALSE, message=FALSE, fig.cap="Work status"}
work_status <-
  ghana %>%
  filter(character=="Work_status") %>%
  mutate(
    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
  )

work_status_tb<-
  tibble(
    background =
      c(""),
    child_under_six = 
      c("")
  )

for (r in 1:nrow(work_status)){
  status <- work_status$background[r]
  work <-
    tibble(
      background = 
        c(
          rep(status, work_status$number_of_employed_women[r])
        ),
      child_under_six = 
        c(
          rep("No_child_under_six", work_status$no_child_under_six[r]),
          rep("One_more_child_under_six", work_status$one_more_child_under_six[r])
        )
      )

  work_status_tb <- bind_rows(work_status_tb, work)
  rm(status,
     work)
}
rm(r)
work_status_tb <- work_status_tb[-c(1),]

work_status_tb <-
  work_status_tb %>%
  mutate(
    background = factor(background,
                        levels = c('For_family_member',
                                   'For_someone_else',
                                   'Self-employed')
                        )
    )

work_status_tb %>%
  ggplot(mapping=aes(x=background, fill=child_under_six)) +
  geom_bar(position='dodge') +
  theme_minimal() +
  labs(x='Work status', y='number of employed', fill='Child under six') +
  scale_x_discrete(labels = c("For_family_member" = "For family member",
                              "For_someone_else" = "For someone else")) + 
  scale_fill_discrete(labels = c("No child under six", 
                                 "One or more child under six"))

rm(work_status_tb)
```

Figure \@ref(fig:workstatus) shows that

```{r workstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
work_status <-
  work_status %>%
  mutate(
    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
    ) %>%
  mutate(
    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
  ) %>%
  select(-caretaker_other_male_child) %>%
  rename(caretaker_other_child = caretaker_other_female_child)

work_status_tb<-
  tibble(
    background =
      c(""),
    child_caretaker = 
      c("")
  )

work_status[1, 13] <- 0
work_status[2, 13] <- 0
work_status[3, 13] <- work_status[3, 13] + 1

for (r in 1:nrow(work_status)){
  status <- work_status$background[r]
  work <-
    tibble(
      background = 
        c(
          rep(status, work_status$one_more_child_under_six[r])
        ),
      child_caretaker = 
        c(
          rep("respondent", work_status$caretaker_respondent[r]),
          rep("partner", work_status$caretaker_partner[r]),
          rep("other_relative", work_status$caretaker_other_relative[r]),
          rep("neighbor", work_status$caretaker_neighbor[r]),
          rep("hired", work_status$caretaker_hired[r]),
          rep("child_in_school", work_status$caretaker_child_in_school[r]),
          rep("other_child", work_status$caretaker_other_child[r]),
          rep("not_worked_since_birth", work_status$caretaker_not_worked_since_birth[r]),
          rep("other", work_status$caretaker_other[r]),
          rep("missing", work_status$caretaker_missing[r])
        )
      )

  work_status_tb <- bind_rows(work_status_tb, work)
  rm(status,
     work)
}
rm(r)
work_status_tb <- work_status_tb[-c(1),]

work_status_tb <-
  work_status_tb %>%
  mutate(
    background = factor(background,
                        levels = c('For_family_member',
                                   'For_someone_else',
                                   'Self-employed')
                        ),
    child_caretaker = factor(child_caretaker,
                             levels = c('respondent',
                                        'partner',
                                        'other_relative',
                                        'neighbor',
                                        'hired',
                                        'child_in_school',
                                        'other_child',
                                        'not_worked_since_birth',
                                        'other',
                                        'missing')
                             )
    )

work_status_tb %>%
  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
  geom_bar() +
  theme_minimal() +
  labs(x='',
       caption = 'Respondent is currently employed but has not worked since last birth.') +
  theme(axis.text.x = element_text(angle=15), legend.position='none') +
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent", 
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired",
        "child_in_school" = "schooling",
        "other_child" = "siblings",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  ) +
  facet_wrap(vars(background),
             dir = "v",
             scales = "free",
             labeller = labeller(background = c("For_family_member" = "For family member",
                                                "For_someone_else" = "For someone else",
                                                "Self-employed" = "Self-employed")
                                 )
  )

rm(work_status_tb)
```

## Occupation

```{r occupation, echo=FALSE, message=FALSE, fig.cap="Occupation"}
occupation <-
  ghana %>%
  filter(character=="Occupation") %>%
  mutate(
    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
  )

occupation_tb<-
  tibble(
    background =
      c(""),
    child_under_six = 
      c("")
  )

for (r in 1:nrow(occupation)){
  type <- occupation$background[r]
  occup <-
    tibble(
      background = 
        c(
          rep(type, occupation$number_of_employed_women[r])
        ),
      child_under_six = 
        c(
          rep("No_child_under_six", occupation$no_child_under_six[r]),
          rep("One_more_child_under_six", occupation$one_more_child_under_six[r])
        )
      )

  occupation_tb <- bind_rows(occupation_tb, occup)
  rm(type,
     occup)
}
rm(r)
occupation_tb <- occupation_tb[-c(1),]

occupation_tb <-
  occupation_tb %>%
  mutate(
    background = factor(background,
                        levels = c('Agricultural',
                                   'Nonagricultural')
                        )
    )

occupation_tb %>%
  ggplot(mapping=aes(x=background, fill=child_under_six)) +
  geom_bar(position='dodge') +
  theme_minimal() +
  labs(x='work status', y='number of employed', fill='Child under six') +
  scale_fill_discrete(labels = c("No child under six", 
                                 "One or more child under six"))

rm(occupation_tb)
```

Figure \@ref(fig:occupation) shows that

```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
occupation <-
  occupation %>%
  mutate(
    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
    ) %>%
  mutate(
    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
  ) %>%
  select(-caretaker_other_male_child) %>%
  rename(caretaker_other_child = caretaker_other_female_child)

occupation_tb<-
  tibble(
    background =
      c(""),
    child_caretaker = 
      c("")
  )

occupation[2, 13] <- occupation[2, 13] + 1

for (r in 1:nrow(occupation)){
  type <- occupation$background[r]
  occup <-
    tibble(
      background = 
        c(
          rep(type, occupation$one_more_child_under_six[r])
        ),
      child_caretaker = 
        c(
          rep("respondent", occupation$caretaker_respondent[r]),
          rep("partner", occupation$caretaker_partner[r]),
          rep("other_relative", occupation$caretaker_other_relative[r]),
          rep("neighbor", occupation$caretaker_neighbor[r]),
          rep("hired", occupation$caretaker_hired[r]),
          rep("child_in_school", occupation$caretaker_child_in_school[r]),
          rep("other_child", occupation$caretaker_other_child[r]),
          rep("not_worked_since_birth", occupation$caretaker_not_worked_since_birth[r]),
          rep("other", occupation$caretaker_other[r]),
          rep("missing", occupation$caretaker_missing[r])
        )
      )

  occupation_tb <- bind_rows(occupation_tb, occup)
  rm(type,
     occup)
}
rm(r)
occupation_tb <- occupation_tb[-c(1),]

occupation_tb <-
  occupation_tb %>%
  mutate(
    background = factor(background,
                        levels = c('Agricultural',
                                   'Nonagricultural')
                        ),
    child_caretaker = factor(child_caretaker,
                             levels = c('respondent',
                                        'partner',
                                        'other_relative',
                                        'neighbor',
                                        'hired',
                                        'child_in_school',
                                        'other_child',
                                        'not_worked_since_birth',
                                        'other',
                                        'missing')
                             )
    )

occupation_tb %>%
  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
  geom_bar() +
  theme_minimal() +
  labs(x='',
       caption = 'Respondent is currently employed but has not worked since last birth.') +
  theme(axis.text.x = element_text(angle=15), legend.position='none') + 
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent", 
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired",
        "child_in_school" = "schooling",
        "other_child" = "siblings",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  ) +
  facet_wrap(vars(background),
             dir = "v",
             scales = "free")

rm(occupation_tb)
```

## Employment status

```{r employmentstatus, echo=FALSE, message=FALSE, fig.cap="Employment status"}
employment_status <-
  ghana %>%
  filter(character=="Employment_status") %>%
  mutate(
    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
  )

employment_status_tb<-
  tibble(
    background =
      c(""),
    child_under_six = 
      c("")
  )

for (r in 1:nrow(employment_status)){
  status <- employment_status$background[r]
  employment <-
    tibble(
      background = 
        c(
          rep(status, employment_status$number_of_employed_women[r])
        ),
      child_under_six = 
        c(
          rep("No_child_under_six", employment_status$no_child_under_six[r]),
          rep("One_more_child_under_six", employment_status$one_more_child_under_six[r])
        )
      )

  employment_status_tb <- bind_rows(employment_status_tb, employment)
  rm(status,
     employment)
}
rm(r)
employment_status_tb <- employment_status_tb[-c(1),]

employment_status_tb <-
  employment_status_tb %>%
  mutate(
    background = factor(background,
                        levels = c('All_year_full_week',
                                   'All_year_part_week',
                                   'Seasonal',
                                   'Occasional')
                        )
    )

employment_status_tb %>%
  ggplot(mapping=aes(x=background, fill=child_under_six)) +
  geom_bar(position='dodge') +
  theme_minimal() +
  labs(x='Work status', y='number of employed', fill='Child under six') +
  scale_x_discrete(labels = c("All_year_full_week" = "All year, full week",
                              "All_year_part_week" = "All year, part week")) +
  theme(axis.text.x = element_text(angle=15)) +
  scale_fill_discrete(labels = c("No child under six", 
                                 "One or more child under six"))

rm(employment_status_tb)
```

Figure \@ref(fig:employmentstatus) shows that

```{r employment_statuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
employment_status <-
  employment_status %>%
  mutate(
    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
    ) %>%
  mutate(
    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
  ) %>%
  select(-caretaker_other_male_child) %>%
  rename(caretaker_other_child = caretaker_other_female_child)

employment_status_tb<-
  tibble(
    background =
      c(""),
    child_caretaker = 
      c("")
  )

employment_status[3,13] <- employment_status[3,13] - 1

for (r in 1:nrow(employment_status)){
  status <- employment_status$background[r]
  employment <-
    tibble(
      background = 
        c(
          rep(status, employment_status$one_more_child_under_six[r])
        ),
      child_caretaker = 
        c(
          rep("respondent", employment_status$caretaker_respondent[r]),
          rep("partner", employment_status$caretaker_partner[r]),
          rep("other_relative", employment_status$caretaker_other_relative[r]),
          rep("neighbor", employment_status$caretaker_neighbor[r]),
          rep("hired", employment_status$caretaker_hired[r]),
          rep("child_in_school", employment_status$caretaker_child_in_school[r]),
          rep("other_child", employment_status$caretaker_other_child[r]),
          rep("not_worked_since_birth", employment_status$caretaker_not_worked_since_birth[r]),
          rep("other", employment_status$caretaker_other[r]),
          rep("missing", employment_status$caretaker_missing[r])
        )
      )

  employment_status_tb <- bind_rows(employment_status_tb, employment)
  rm(status,
     employment)
}
rm(r)
employment_status_tb <- employment_status_tb[-c(1),]

employment_status_tb <-
  employment_status_tb %>%
  mutate(
    background = factor(background,
                        levels = c('All_year_full_week',
                                   'All_year_part_week',
                                   'Seasonal',
                                   'Occasional')
                        ),
    child_caretaker = factor(child_caretaker,
                             levels = c('respondent',
                                        'partner',
                                        'other_relative',
                                        'neighbor',
                                        'hired',
                                        'child_in_school',
                                        'other_child',
                                        'not_worked_since_birth',
                                        'other',
                                        'missing')
                             )
    )

employment_status_tb %>%
  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
  geom_bar() +
  theme_minimal() +
  labs(x='',
       caption = 'Respondent is currently employed but has not worked since last birth.') +
  theme(axis.text.x = element_text(angle=15), legend.position='none') +
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent",
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired",
        "child_in_school" = "schooling",
        "other_child" = "siblings",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  ) +
  facet_wrap(vars(background),
             dir = "v",
             scales = "free",
             labeller = labeller(background = c("All_year_full_week" = "All year, full week",
                                                "All_year_part_week" = "All year, part week",
                                                "Seasonal" = "Seasonal",
                                                "Occasional" = "Occasional")
                                 )
  )

rm(employment_status_tb)
```

# Discussions

## Limitation and weaknesses

The number does not add up to 100. (truncation error)
